### 2023-01-18 paper.tex
Feedback for Section VII

	\section{Analysis of the repository}
	In the previous section, it was mentioned that crawling GitHub might lead to distortions in the dataset. This section presents a short quantitative analysis of a sample of the database generated during experimentation. As written in Section~\ref{sec:implementation}, we were able to generate a corpus of 163,961 Solidity files, which were the results of 299,20437 commits to Github.

	Figure~\ref{fig:versions} shows the distribution of the number of versions of the collected files. The absolute frequency of occurrence of the number of versions are represented in the graph. The scale of the Y-axis is logarithmic and the data point at 200 versions included all files that have 200 or more versions, in order to improve the readability of the graph. 132519 out of 163931 or around 80\% of the files have only 2 versions. It is evident that only a few smart contracts include more than 100 versions of the source code. In spite of that 31412 files have multiple versions. This provides a reasonably large dataset for code mining.

@@

	When collecting data from GitHub, in the first phase, only the repositories containing Solidity source files were collected. This was followed by scraping all Solidity source files from each of those repositories. This order ensured that all relevant files of each repository were accessed, since the GitHub search API does not return all relevant files by simple content search. As a consequence, all 162931 files in the database come from the same 1021 repositories. To investigate this further, the distribution of files per repository was calculated (see Figure~\ref{fig:number}). This diagram shows the absolute frequency of the number of files that being to a particular repository. The Y-axis is again logarithmic and the data point at 500 includes all repositories having 500 or more relevant files. The repository \textit{ethereum/solidity-fuzzing-corpus} contributed the largest number of files - 33145 - to the repository. 29947 files come from the repository \textit{tintinweb/smart-contract-sanctuary-ethereum}. Additionally, the mean of the distribution is at 160 while the standard deviation is 1514. This shows that a few large repositories have a large impact on the dataset, and consequently, on the quality of source code in it. 13.7\% of the repositories contribute only 3 files. But the high standard deviation captures the widely varying numbers of files contributed by repositories. The outlier of exactly 290 Solidity files that are present in 9 different repositories seems to originate from a specific Solidity tutorial project called \textit{cryptozombies}\footnote{https://cryptozombies.io} that was forked by multiple users on GitHub.
	\begin{figure}[!h]
		\centering
		\includegraphics[scale=0.3]{distr_files_repos.png}
		\caption{Distribution of the number of files in the GitHub repositories}
		\label{fig:number}
	\end{figure}

>>>>

	\section{Analysis of the repository}
	In the previous section, it was mentioned that crawling GitHub might lead to distortions in the dataset. This section presents a short quantitative analysis of a sample of the database generated during experimentation. As written in Section~\ref{sec:implementation}, we were able to generate a corpus of 163,961 Solidity files, which were the results of 299,20437\todo{Something is wrong with this number} commits to Github.

	Figure~\ref{fig:versions} shows the distribution of the number of versions of the collected files. The absolute frequency of occurrence of the number of versions are represented in the graph. The scale of the Y-axis is logarithmic and the data point at 200 versions includes all files that have 200 or more versions, in order to improve the readability of the graph. 132,519 out of 163,931 or around 80\% of the files have only 2 versions. It is evident that only a few smart contracts include more than 100 versions of the source code. In spite of that, 31,412 files have multiple versions. This provides a reasonably large dataset for code mining.

@@

	When collecting data from GitHub, in the first phase, only the repositories containing Solidity source files were collected. This was followed by scraping all Solidity source files from each of those repositories. This order ensured that all relevant files of each repository were accessed, since the GitHub search API does not return all relevant files by simple content search. As a consequence, all 162,931 files in the database come from the same 1,021 repositories. To investigate this further, the distribution of files per repository was calculated (see Figure~\ref{fig:number}). This diagram shows the absolute frequency of the number of files that being\todo{"that being''?} to a particular repository. The Y-axis is again logarithmic and the data point at 500 includes all repositories having 500 or more relevant files. The repository \textit{ethereum/solidity-fuzzing-corpus} contributed the largest number of files -- 33,145 -- to the repository. 29,947 files come from the repository \textit{tintinweb/smart-contract-sanctuary-ethereum}. Additionally, the mean of the distribution is at 160 while the standard deviation is 1,514. This shows that a few large repositories have a large impact on the dataset, and consequently, on the quality of source code in it. 13.7\% of the repositories contribute only 3 files. But the high standard deviation captures the widely varying numbers of files contributed by repositories. The outlier of exactly 290 Solidity files that are present in nine different repositories seems to originate from a specific Solidity tutorial project called \textit{cryptozombies}\footnote{https://cryptozombies.io} that was forked by multiple users on GitHub.
	\begin{figure}[!h]
		\centering
		\includegraphics[scale=0.3]{distr_files_repos.png}
		\caption{Distribution of the number of files in the GitHub repositories}
		\label{fig:number}
	\end{figure}
